---
title: "p8105_hw1_fs2757.Rm"
author: "FEI SUN"
date: "2021/9/21"
output: github_document
---

```{r setup}

library(tidyverse)

```

###Problem 1
* Create a data frame comprised of:
  * a random sample of size 10 from a standard Normal distribution
  * a logical vector indicating whether elements of the sample are greater than 0
  * a character vector of length 10
  * a factor vector of length 10, with 3 different factor “levels”

```{r}
##Frame
set.seed(1)

P1_df = tibble(
  random_sample = rnorm(10),
  sample_logical = random_sample > 0,
  character_vector= c("circle","quadrangle","Triangular","rectangle","trapezoid", "square","oval","conical","hexagon","Egg-Shaped"),
  factor_vector= factor(c("S", "S","S","M", "M","M", "L","L","L","L"))
)
```

```{r}
##Mean
mean(pull(P1_df, random_sample))
mean(pull(P1_df, sample_logical))
mean(pull(P1_df, character_vector))
mean(pull(P1_df, factor_vector))

```
** In this case, I could not get the mean of character_vector and factor_vector since they are not numeric or logical.

```{r}
##By using as.numeric function
as.numeric(pull(P1_df, sample_logical))
as.numeric(pull(P1_df, character_vector))
as.numeric(pull(P1_df, factor_vector))
```




