---
title: "p8105_hw1_fs2757.Rm"
author: "FEI SUN"
date: "2021/9/21"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

#Problem 1
* Create a data frame comprised of:
  * a random sample of size 10 from a standard Normal distribution
  * a logical vector indicating whether elements of the sample are greater than 0
  * a character vector of length 10
  * a factor vector of length 10, with 3 different factor “levels”

```{r create data frame}
##Frame
set.seed(1)

P1_df = tibble(
  random_sample = rnorm(10),
  sample_logical = c(random_sample > 0),
  character_vector= c("circle","quadrangle","Triangular","rectangle","trapezoid", "square","oval","conical","hexagon","Egg-Shaped"),
  factor_vector= factor(c("S", "S","S","M", "M","M", "L","L","L","L"))
)
```

```{r}
##Mean
mean(pull(P1_df, random_sample))
mean(pull(P1_df, sample_logical))
mean(pull(P1_df, character_vector))
mean(pull(P1_df, factor_vector))
```
** In this case, I could not get the mean of character_vector and factor_vector since they are not numeric or logical.**

```{r}
##By using as.numeric function to convert
as.numeric(pull(P1_df, sample_logical))
as.numeric(pull(P1_df, character_vector))
as.numeric(pull(P1_df, factor_vector))
```
** In this case, it can be see that logical and factor could convert variables to numerical variable and the character can not convert to numerical variable.**

```{r}
##Converting
as.numeric(as.factor(P1_df$character_vector))
```
** In this case, it can be see that the character can be convert to numerical.**

#Problem 2
* This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.
**install a package containing the penguins dataset.
```{r}
library(palmerpenguins)
```

```{r}
data("penguins", package = "palmerpenguins")
?name
```

*Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:
  * the data in this dataset, including names / values of important variables
  * the size of the dataset (using nrow and ncol)
  * the mean flipper length
  
